Cluster Difference Imaging Photometric Survey. III. An Open Cluster With a 300\,pc Halo

### 2021-02-11 cluster_paper/ms.tex
lithium: minor plot updates

% Context, aims, methods, results, conclusions.
\begin{abstract}
  Recent analyses of the Gaia data have reported the existence of
  diffuse stellar populations surrounding nearby open clusters.  The
  stars in these halos could have escaped from the cores of the
  cluster, or they could be remnants of a star formation complex that
  has since dispersed.  They could also be field stars---false
  positives from overly aggressive clustering algorithms.  In this
  study, we focus on a halo with a length of 300\,pc reported around
  the $\approx$120\,Myr open cluster NGC\,2516.  The classical tidal
  radius of the cluster is $\sim$10\,pc.  Using photometry from Gaia,
  rotation periods from TESS, and lithium measurements from Gaia-ESO
  and GALAH, we find that the halo of NGC\,2516 is real and coeval
  with the core.  Two in three kinematically selected halo members
  25-250\,pc from the cluster center show rotation periods consistent
  with a gyrochronological age of 120\,Myr.  A comparison sample of
  field stars shows no such trend.  The rotation period and lithium
  abundance for the cluster stars are also anti-correlated at fixed
  stellar mass, as is the case with comparable stellar populations.
  This work expands the set of confirmed NGC\,2516 members by a factor
  of $\approx$2, and quantifies the degree to which Gaia-based
  analyses can identify dispersed stellar populations against a
  background of field star contaminants.  We highlight implications
  for spectroscopic survey targeting, open cluster dispersal, and
  planet searches around young stars.
\end{abstract}

>>>>

% Context, aims, methods, results, conclusions.
\begin{abstract}
  Recent analyses of the Gaia data have reported the existence of
  diffuse stellar populations surrounding nearby open clusters.  The
  stars in these halos could have escaped from the cores of the
  cluster, or they could be remnants of a star formation complex that
  has since dispersed.  They could also be field stars---false
  positives from overly aggressive clustering algorithms.  In this
  study, we focus on a halo with a length of 300\,pc reported around
  the $\approx$120\,Myr open cluster NGC\,2516.  The classical tidal
  radius of the cluster is $\sim$10\,pc.  Using photometry from Gaia,
  rotation periods from TESS, and lithium measurements from Gaia-ESO
  and GALAH, we find that the halo of NGC\,2516 is real and coeval
  with the core.  Two in three kinematically selected halo members
  25-250\,pc from the cluster center show rotation periods consistent
  with a gyrochronological age of 120\,Myr.  A comparison sample of
  field stars shows no such trend.  The rotation period and lithium
  abundances of the cluster stars are also anti-correlated at fixed
  stellar mass, as is the case with comparable stellar populations.
  This work expands the set of confirmed NGC\,2516 members by a factor
  of $\approx$2, and quantifies the degree to which Gaia-based
  analyses can identify dispersed stellar populations against a
  background of field star contaminants.  We highlight implications
  for spectroscopic survey targeting, open cluster dispersal, and
  planet searches around young stars.
\end{abstract}
